Minimizing post shock forecasting error using disparate information

### 2020-06-06 manuscript/manuscript.tex
updated data analysis, discussions, tables for parametric bootstrap

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=1in}

@@

\begin{enumerate}
  \item The synthetic intervention paper and comment are added in the introduction. Other parts haven't been revised.
  \item SCM.R for SCM method and sim.R for simulation are added in Github.
  \item Data analysis references are fixed. The structure is organized better.
\end{enumerate}

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} .
\end{align*}
where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix}, \ldots, \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} \right\}.
 \end{align*}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
  \end{align*}
%Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

@@

In this section, we present a bootstrap procedure 
%(see Section \ref{modelsetup}) 
that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions. However, the pseudo time series generated by this procedure are not stationary. (\textbf{Is this necessary to state? There needs to be a rationale fro why this is not a problem.})

@@

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}

In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession. Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020. We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock. The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool. %Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.

@@

\begin{enumerate}
\item[(1)] {\bf AR(1) model and time window}. We will use a simple AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}. We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
\item[(3)] {\bf Construction of donor pool}. Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
several events in September, 2008, and November 27, 2014. The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}. The reasons for those three shocks are:
  \begin{enumerate}
  \item On September 11th, 2001, Islamic extremist al-Qaeda committed a series of terrorist attacks against the United States of America \citep{braniff2011towards}. In addition to the tragic loss of life, this triggered negative repercussions on the U.S. and world economies with falling stock prices and a falling U.S. dollar \citep{floyd2001terror}. Moreover, trading was closed until September 17, 2001 \citep{johnston2006impact}.
  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
  \end{enumerate}
%\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
\end{enumerate}

@@

{\bf Jilei, can you add the weighted adjustment estimator to this analysis?}
We estimate the five shock effects mentioned above using OLS and then construct $\hat{\alpha}_{\text{adj}}$ and $\hat{\alpha}_{\text{IVW}}$ from these estimates. We also consider estimation without the September 11th, 2001 shock effect since there was a week long delay in trading due to the terrorist attack.

\begin{figure}
  \begin{center}
    \includegraphics[height = 8cm]{CPtimeseries.png}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price. The blue line displays the }
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure}

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects.
The unadjusted forecast had an RMSE of 12.24, 
the use of $\hat{\alpha}_{\text{adj}}$ had an RMSE of 6.85,
the use of $\hat{\alpha}_{\text{adj}}$ without September 11th had an RMSE of 5.96,
the use of $\hat{\alpha}_{\text{IVW}}$ had an RMSE of 9.37,
and the use of $\hat{\alpha}_{\text{IVW}}$ without September 11th had an RMSE of 6.15.

We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.80.  The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects without September 11th has an RMSE of 0.023.

@@

>>>>

% use packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{amscd}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{enumitem}
\usepackage{url}
\usepackage{authblk}
\usepackage{bm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{caption}
\usepackage{float}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
% margin setup
\geometry{margin=1in}

@@

\begin{enumerate}
  \item Remark for non-uniqueness of $\mathbf{W}^*$ is added in Section \ref{properties}.
  \item Generalizations are added in Section 6
  \item Data analysis is updated with results of weighted adjustment estimators
  \item Some preliminary setup of the simulation is added in Section 4.
\end{enumerate}

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate 
our weighted-adjustment estimator. Consider a $n\times 1$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \begin{pmatrix}
    \mbf{x}_{1, T_1^*} \\ \mbf{x}_{1, T_1^*+1}
  \end{pmatrix}
  \quad \text{ and }
  \quad  \hat{\mbf{X}}_1(\mbf{W})
  = w_2\begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix} + \cdots + w_{n+1} \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} .
\end{align*}
where $\mbf{X}_1$ and $\hat{\mbf{X}}_1(\mbf{W})$ are $2 \times p$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon w_2+ \cdots + w_{n+1}=1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \begin{pmatrix}
     \mbf{x}_{2, T_2^*} \\
      \mbf{x}_{2, T_2^*+1}
   \end{pmatrix}, \ldots, \begin{pmatrix}
     \mbf{x}_{n+1, T_{n+1}^*} \\
      \mbf{x}_{n+1, T_{n+1}^*+1}
   \end{pmatrix} \right\}.
 \end{align*}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})\big)}_{2p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
We stress that $\mathbf{W}^*$ may not be unique. \cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}.
  \end{align*}
 %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock-effects. 
Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

\begin{remark}
  In Section \ref{constructionofestimators}, we note that $\mathbf{W}^*$ may not be unique. However, Proposition \ref{proprisk} and \ref{propriskwadj2} will hold for  every $\hat{\alpha}_{\rm wadj}$ using  $\mathbf{W}^*$ that satisfies (\ref{SCM}).
\end{remark}

@@

In this section, we present a bootstrap procedure 
%(see Section \ref{modelsetup}) 
that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

@@

In this section, we provide experiments that vary across variance of $\alpha_i$, $y_{i,t}$, and donor pool size $n$ using two bootstrap techniques with one conditioned on the donor pool and one without. We implement our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$. We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers. It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Moreover, $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$.

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}
In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession. Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020. We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock. The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool. %Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.

@@

\begin{enumerate}
\item[(1)] {\bf AR(1) model and time window}. We will use a simple AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}. We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
\item[(3)] {\bf Construction of donor pool}. Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
several events in September, 2008, and November 27, 2014. The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}. The reasons for those three shocks are:
  \begin{enumerate}
  \item On September 11th, 2001, Islamic extremist al-Qaeda committed a series of terrorist attacks against the United States of America \citep{braniff2011towards}. In addition to the tragic loss of life, this triggered negative repercussions on the U.S. and world economies with falling stock prices and a falling U.S. dollar \citep{floyd2001terror}. Moreover, trading was closed until September 17, 2001 \citep{johnston2006impact}.
  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
  \end{enumerate}
%\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
We assume that the five shocks are independent of the shock that Conoco Phillips  experienced on 2020-03-09.
\end{enumerate}

@@

\vspace{-.3cm}
\begin{table}[H]
  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
  \begin{center}
    \begin{tabular}{ccrrrrrr}
       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
             \hline 
2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
  2008 Mar.  & 03--17 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
 \multirow{3}{*}{2008 Sep.}
 & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
 & $T_4^* +1 = \text{09--12}$ \\
   & $T_5^* +1 = \text{09--26}$ \\
\\
  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
    \end{tabular}
  \end{center}  \vspace{-.3cm}
\end{table}

Table \ref{table1} presents some basic summary statistics for the covaraites and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool. Note that there are three shock-effects nested in the time series 2008 September. This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool. Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.

We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. Table \ref{table1} that contains some basic summary statistics for the units and range of the covariates can provide some information about the performance of the fit. The fit is acceptable. According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately.

$\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (2008--09--08) and $\alpha_5$ (2014--11--27) according to the setup of $\mc{M}_2$. That is, the shock that Conoco Phillips experienced in 2020-03-09 is similar to the shock induced by the placement of Fannie May and Freddie Mac, and the one caused by oil supply shock on 2014--11--27. It is consistent with discussion at the beginning of the section.
\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    Risk-reduction proposition & 1 & 1 & 1 \\
    Best shock-effect estimator & 0 & 0 & 1
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. Note that this parametric bootstrap procedure is conditioned  on the  donor pool. Table \ref{table2} tells that all three proposed  shock-effect estimators are usable in the sense that the forecast employing them is better than the one without; and the $\hat{\alpha}_{\rm wadj}$ is the best in terms of the estimated risk-reduction quantity. Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

\begin{figure}
  \begin{center}
    \includegraphics[height = 9cm]{fig2.pdf}
    \caption{March 9th, 2020 post-shock forecasts for Conoco Phillips stock price.}
    \label{Fig:CP}
  \end{center}  
  \vspace{-.6cm}
\end{figure}

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 9.870 whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of 4.475,  4.432, and 4.741, respectively.
Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without, and that $\hat{\alpha}_{\rm wadj}$ is the best with lowest RMSE.

We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects without September 11th have  RMSEs of $1.341$, $1.677$, and $0.661$, respectively.

@@

Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models. First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.  The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method. Second, multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent. This generalization was adopted in Section \ref{forecasting}. In this case, the variance expressions proposed in Section \ref{properties} will not work. However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest. Third, though it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments. Fourth, the covariates in the model for $\alpha_i$ in $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$. It is because in the derivation such dependence is not used.
